Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-05-29 paper.tex
replaced figures
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
added comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
new changes to repo including machine learning

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The dependency on the correct operation of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control, health care, surveillance, mobile devices, telecommunications, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory and sophisticated software modules, in order to meet increasing computational power and flexibility demands. As a consequence, reliability of embedded (distributed) software becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation. Nonetheless, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, validating operation logic, ensuring correct behavior, providing compliance with the target system, and supporting new software architectures and legacy designs (usually written in low-level languages). The present research discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding embedded systems. Reliability issues, in the development of micro-grids and cyber-physical systems, are then considered, as a prominent verification and synthesis application for achieving a \textit{correct-by-construction} design.
\end{abstract}

@@

@@

The goals of the present article is to briefly present part of the established research and also clarify the current trends, which are mainly driven by CPSs and IoT. We present a brief discussion about models for CPS, in Section \ref{sec:model}, and then cover preliminaries on bounded model checking, \textit{k}-induction verification based on invariant inference, and counter-example guided inductive synthesis, in Section~\ref{Preliminaries}. In Section~\ref{Verification-Challenges}, the main challenges regarding the verification and synthesis of embedded systems are described, while Section~\ref{Research-Problem} tackles those challenges that are (partially) open in current published research. Section \ref{Newapp} then addresses new applications, which take into account the new trends mentioned here, and Section~\ref{achievements} describes current achievements and future trends in verification and synthesis of embedded systems. Finally, we conclude and describe future work in Section~\ref{conclusions}.

@@

The correctness specification $\sigma$ provided to the program synthesizer is of the form $\exists \vec{F} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free formula typically supported by SMT solvers. The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part. The {\sc Synthesize} and {\sc Verify} phases interact via a finite set of test vectors {\sc inputs} that is updated incrementally. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, this witness is a candidate solution to the full synthesis formula, which is passed to the {\sc verify} phase, in order to check whether it is a full solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates; otherwise, additional information is provided to the {\sc synthesize} phase, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again. 
%
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.12]{figure4.eps}
	\caption{Counter-Example Guided Inductive Synthesis.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}

@@

Generally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation~\cite{Behrend15,Lettnin09}, as shown in Figure~\ref{verification-methodologies}. 
%
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.35]{figure3.eps}
	\caption{Verification methodologies for embedded systems.}
	\label{verification-methodologies}
\end{figure}

@@

@@

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The dependency on the correct operation of embedded systems is rapidly growing, mainly due to their wide range of applications, such as micro-grids, automotive device control, health care, surveillance, mobile devices, telecommunications, and consumer electronics. Their structures are becoming more and more complex and now require multi-core processors with scalable shared memory and sophisticated software modules, in order to meet increasing computational power, flexibility demands, and adaptation to new scenarios and behaviors. As a consequence, reliability of embedded (distributed) software becomes a key issue during system development, which must be carefully addressed and assured. Normally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation. Nonetheless, other additional challenges have been raised: the need for meeting time and energy constraints, handling concurrent software, dealing with platform restrictions, evaluating implementation-structure choices, validating operation logic, ensuring correct behavior, providing compliance with the target system, incorporating knowledge about new problems and conditions, and supporting new software architectures and legacy designs (usually written in low-level languages). The present research discusses challenges, problems, and recent advances to ensure correctness and timeliness regarding embedded systems. Reliability issues, in the development of micro-grids and cyber-physical systems, are then considered, as a prominent verification and synthesis application for achieving a \textit{correct-by-construction} design.
\end{abstract}

@@

Regarding behavior correctness, one important observation is that it is becoming more difficult, since fixed mathematical models are being replaced by machine learning approaches (ML) \cite{mlembe}, where future operation may be change based on data acquired during previous actions, due to model updating. As a consequence, system correctness verification procedures should also adapt somehow and incorporate new checks.

@@

The goals of the present article is to briefly present part of the established research and also clarify the current trends, which are mainly driven by CPSs, IoT, and ML. We present a brief discussion about models for CPS, in Section \ref{sec:model}, and then cover preliminaries on bounded model checking, \textit{k}-induction verification based on invariant inference, and counter-example guided inductive synthesis, in Section~\ref{Preliminaries}. In Section~\ref{Verification-Challenges}, the main challenges regarding the verification and synthesis of embedded systems are described, while Section~\ref{Research-Problem} tackles those challenges that are (partially) open in current published research. Section \ref{Newapp} then addresses new applications, which take into account the new trends mentioned here, and Section~\ref{achievements} describes current achievements and future trends in verification and synthesis of embedded systems. Finally, we conclude and describe future work in Section~\ref{conclusions}.

@@

The correctness specification $\sigma$ provided to the program synthesizer is of the form $\exists \vec{F} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{F})$, where $\vec{F}$ ranges over functions, $\vec{x}$ ranges over ground terms, and $\sigma$ is a quantifier-free formula typically supported by SMT solvers. The ground terms are interpreted over some finite domain $\mathcal{D}$, where $\mathcal{D}$ can be encoded using the SMT's bit-vectors part. The {\sc Synthesize} and {\sc Verify} phases interact via a finite set of test vectors {\sc inputs} that is updated incrementally. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, this witness is a candidate solution to the full synthesis formula, which is passed to the {\sc verify} phase, in order to check whether it is a full solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates; otherwise, additional information is provided to the {\sc synthesize} phase, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again. 
%
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.12]{figure3.eps}
	\caption{Counter-Example Guided Inductive Synthesis.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}

@@

Generally, state-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation~\cite{Behrend15,Lettnin09}, as shown in Figure~\ref{verification-methodologies}. 
%
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.35]{figure4.eps}
	\caption{Verification methodologies for embedded systems.}
	\label{verification-methodologies}
\end{figure}

@@

\textcolor{red}{We still have to mention RP7...}

@@

%1
\bibitem{mlembe}
S.~Virtanen:
\newblock {\em {Advancing Embedded Systems and Real-Time Communications with Emerging Technologies}}.
\newblock IGI Global, ISBN 978-1466660342, pp. 1--502, 2014.
